Democracy, Public Support, and Measurement Uncertainty

### 2021-05-04 paper/dcpo_demsupport.Rmd
replicated the gmm for ajps

estimate_cls <- function(aModel, aType = "pooling") {
  if (aType == "gmm") {
    result_cls_1k <- map(df_cls, function(aDataset) {
      pgmm(
        as.formula(aModel),
        effect = "individual",
        model = "onestep",
        transformation = "ld",
        indexes = c("Country", "Year"),
        data = aDataset
      )
    })

    result_vars_cls_1k <-
      mitools::MIextract(result_cls_1k, fun = vcovHC_se)

  } else {
    result_cls_1k <- map(df_cls, function(aDataset) {
      plm::plm(aModel,
               model = "pooling",
               data = aDataset)
    })

    result_vars_cls_1k <-
      mitools::MIextract(result_cls_1k, fun = vcovBK_se)
  }

  result_betas_cls_1k <-
    mitools::MIextract(result_cls_1k, fun = coef)

  df_result_cls <-
    summary(
      mitools::MIcombine(results = result_betas_cls_1k, variance = result_vars_cls_1k)
    ) %>% rownames_to_column(var = "term") %>%
    rename(conf.low = `(lower`,
           conf.high = `upper)`,
           estimate = results) %>%
    filter(!str_detect(term, "(Intercept)"))
}

mod_ls <- paste0(
  "Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + ",
  c("plm::lag(theta, 1)", 
    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
  " + plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)"
)

@@

  ## Not work with ifelse
  result_vars <- ifelse(class(result[[1]])[1] == "plm", 
                        eval(mitools::MIextract(result, fun = vcovBK_se)),
                        eval(mitools::MIextract(result, fun = vcovHC_se)))

@@

save(tidy_result_clsUncertain, file = here::here("output", "estimates_clsAJPS.RDS"))
```

```{r dcpoPointAJPS}

ls_country <- levels(dcpo_input$data$kk)
first_year <- min(dcpo_input$data$year)

@@

estimate_dcpo <- function(aModel, aType = "pooling") {
  if (aType == "gmm") {
    result_dcpo_1k <- map(df_dcpo, function(aDataset) {
      pgmm(
        as.formula(aModel),
        effect = "individual",
        model = "onestep",
        transformation = "ld",
        indexes = c("Country", "Year"),
        data = aDataset
      )
    })

    result_vars_dcpo_1k <-
      mitools::MIextract(result_dcpo_1k, fun = vcovHC_se)

  } else {
    result_dcpo_1k <- map(df_dcpo, function(aDataset) {
      plm::plm(aModel,
               model = "pooling",
               data = aDataset)
    })

    result_vars_dcpo_1k <-
      mitools::MIextract(result_dcpo_1k, fun = vcovBK_se)
  }

  result_betas_dcpo_1k <-
    mitools::MIextract(result_dcpo_1k, fun = coef)

  df_result_dcpo <-
    summary(
      mitools::MIcombine(results = result_betas_dcpo_1k, variance = result_vars_dcpo_1k)
    ) %>% rownames_to_column(var = "term") %>%
    rename(conf.low = `(lower`,
           conf.high = `upper)`,
           estimate = results) %>%
    filter(!str_detect(term, "(Intercept)"))
}

mod_ls <- paste0(
  "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
  c("plm::lag(theta, 1)", 
    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
  " + plm::lag(lg_imp_mdpgdp, 1) +
             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)"
)

df_result_dcpoAJPS <- map(mod_ls, estimate_dcpo)

save(df_result_dcpoAJPS, file = here::here("output", "estimates_dcpoAJPS.RDS"))
```

>>>>

@@

  ## Not work with ifelse
  if(class(result[[1]])[1] == "plm"){
      result_vars <- mitools::MIextract(result, fun = vcovBK_se)
  }else{
      result_vars <- mitools::MIextract(result, fun = vcovHC_se)
  }

@@

save(tidy_result_clsUncertain, file = "estimates_clsAJPS.RDS")
```

```{r dcpoPointAJPS}
# Not showing in the final result
ls_country <- levels(dcpo_input$data$kk)
first_year <- min(dcpo_input$data$year)

@@

# estimate_dcpo <- function(aModel, aType = "pooling") {
#   if (aType == "gmm") {
#     result_dcpo_1k <- map(df_dcpo, function(aDataset) {
#       pgmm(
#         as.formula(aModel),
#         effect = "individual",
#         model = "onestep",
#         transformation = "ld",
#         indexes = c("Country", "Year"),
#         data = aDataset
#       )
#     })
#     
#     result_vars_dcpo_1k <-
#       mitools::MIextract(result_dcpo_1k, fun = vcovHC_se)
#     
#   } else {
#     result_dcpo_1k <- map(df_dcpo, function(aDataset) {
#       plm::plm(aModel,
#                model = "pooling",
#                data = aDataset)
#     })
#     
#     result_vars_dcpo_1k <-
#       mitools::MIextract(result_dcpo_1k, fun = vcovBK_se)
#   }
#   
#   result_betas_dcpo_1k <-
#     mitools::MIextract(result_dcpo_1k, fun = coef)
#   
#   df_result_dcpo <-
#     summary(
#       mitools::MIcombine(results = result_betas_dcpo_1k, variance = result_vars_dcpo_1k)
#     ) %>% rownames_to_column(var = "term") %>%
#     rename(conf.low = `(lower`,
#            conf.high = `upper)`,
#            estimate = results) %>%
#     filter(!str_detect(term, "(Intercept)"))
# }
# 
# mod_ls <- paste0(
#   "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
#   c("plm::lag(theta, 1)", 
#     "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
#   " + plm::lag(lg_imp_mdpgdp, 1) +
#              plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
#              plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)"
# )
# 
# df_result_dcpoAJPS <- map(mod_ls, estimate_dcpo)

ls_eq <- glue("Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + {ls_iv} + plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) + plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)")

ls_mod <- c(
    glue("plm({ls_eq}, model = 'pooling', data = aData)"),
    glue(
        "pgmm({ls_eq} | plm::lag(Vdem_libdem, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('Country', 'Year'))"
    )
)

tidy_result_dcpoUncertain <- map(ls_mod, function(aMod){ # reading a model
  result <- map(df_dcpo, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

  ## Not work with ifelse
  if(class(result[[1]])[1] == "plm"){
      result_vars <- mitools::MIextract(result, fun = vcovBK_se)
  }else{
      result_vars <- mitools::MIextract(result, fun = vcovHC_se)
  }

save(tidy_result_dcpoUncertain, file = here::here("output", "estimates_dcpoAJPS.RDS"))
```
